The limits of self commitment and private paternalism \thanks{}

### 2022-02-17 donde.tex
Analysis for email feb16

Pawn loans involve individuals leaving valuable and liquid assets, typically jewelry, as collateral in exchange for an immediate cash loan. Collateral is typically much larger than the loan, which allows lenders to skip the checking of credit history and give the loan immediately. This makes pawn loans popular to get cash to pay for emergencies. In fact, they are one of the most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender alone served more than 1 million clients in the last 3 years with more than 4 million contracts. For comparison there were 2.3 million micro-finance clients in Mexico in 2009 \citep{Pedroza:2010}.

Pawn borrowing is also one of the oldest forms of borrowing. Pawn loans existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago \citep{PawnShops}. In spite of the high prevalence and long history, pawnshop borrowing has not received much attention in the economics literature. The closest product studied is probably payday loans. In developing countries, however, payday lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash. According to \cite{Payday} to get a payday loan: ``All that a prospective borrower typically needs is a home address; a valid checking account; a driver’s license and Social Security number; a couple of pay stubs to verify employment; wages and pay dates; and minimum earnings of at least \$1,000 a month''. Although the author meant this list as an instance of low requirements, they would render virtually all poor households in the developing countries ineligible.

@@

As with payday lending, pawnshop lending is controversial. Regulators have concerns with the sophistication of borrowers using it. The US congress has actually banned the payday lending industry from serving active military personnel, and some States in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}. The main source of concern is whether consumers that use these loans suffer from behavioral and cognitive biases which imply sub-optimal choices. There is some evidence  in support of this view.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one  would not expect additional information disclosure about the payday product to  alter their borrowing behavior'', but to the contrary they find that simply disclosing how financing costs add up reduced demand by 11\%. %\cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.
}

@@

Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period, and the client could make payments at anytime with no penalty for pre-payment. If the client paid the principal plus the accumulated interest in less than 105 days, then she received back her pawn, otherwise the pawnbroker kept the piece and any payments made. Before the contract expired, the client had the right to renew it  using the same collateral for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.  Only 26\% of borrowers renew twice or more. This contract was standard in the industry.

The clients that pawned understood its conditions (as we verified in interviews) and still decided to pawn. \footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and value the convenience of pawn borrowing.The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months. They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.  When asked why they are pawning this piece gr{5\%} responded gr{`lost a family member'}, gr{`a medical emergency'} (gr{11\%}), gr{`an urgent expense'} (gr{71\%}),

Our context is one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.   One potential explanation for high default is that clients are really just selling their gold piece. This is unlikely for several reasons: (a) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (b) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, (c) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}). %(d) there is a lot of engagement with the lender after pawning even for those who lost their pawn. On average clients that lost their pawn paid 34\% of the value of their loan, and close to 42\% of clients extended the loan for another cycle and made payments in the second cycle (see Figure \ref{proxy_naive} in Appendix).
High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer. Lender P was explicitly interested in  partnering with us to investigate whether a frequent payment contract would increase pawn recovery, costumer satisfaction, and repeat borrowing, and to explore whether there was demand for such a contract.

The pawnshop therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans. The interest rate typically used to calculate borrower APRs is thus a very inadequate measure of the effective cost of pawn loans.

@@

\vspace{.2in}
\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that it enhances the regularity and salience of payments. It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was reinforced in two ways; first by reminders issued to any borrower delinquent on the monthly payments that they were supposed to be made, and secondly by the levying of a nominal fee (2\% of minimum due) that would be levied on individuals behind in their payments.\footnote{This fee was set by the lender, being deemed to be large enough to reinforce commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.  In contrast with \cite{John} we don't let the clients choose the size of the fee. That paper shows that doing this results in wrong choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment, as explained in the introduction. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
}

@@

We did not allocate equal number of days across arms, since we were interested in having more power in some of them. The number of branch days allocated to each were 84, 80, 93, 68, and 82, respectively.

\vspace{.2in}
\noindent \textbf{Randomization.}  Starting September 6, 2012, we implemented the experiment in 6 branches of Lender $P$. The branches were selected by Lender $P$ to be dispersed across Mexico city and have varying sizes. In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size. %Thus we eliminated {the smallest} ones. 
Branches are more than 5 km apart from each other, and there is little substitution among them; only 1\% of consumers appear in more than one of our branches.

 Branch personnel did not know which treatment would happen on which day. They were told that there were 5 different ``types of contract-days'' and that the system chose randomly which applied on any given date, and that it could happen for instance that two consecutive dates had the same contract. They were also told that this way of operating was in place in various Lender P's branches (they did not know which ones), and that it could be in place for several months. Randomizing at the day level limits the problem of contamination arising from clients realizing that other clients get different contracts than theirs. It also limits potential manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen. Intra-branch day correlation on the probability of default (ICC) is small, at {0.08}, so we don't lose much power vis-a-vis individual level randomization.

By comparing the \textit{Forced Commitment} arm vs the \textit{Control} arm we estimate the causal effect of mandatory installment frequency that acts as a incentive to pay earlier vis-a-vis the pay-when-you-want contract. On the other hand, having arms where clients can choose among these contracts allows us to study clients' demand for commitment to pay earlier, and the nature of selection into this choice. A neoclassical consumer with no intra-household concerns would not voluntarily restrict her options of payment profiles (as in the monthly installment contract) by being subject to fees, since she can always replicate the monthly payment profile herself under the status quo contract if she so desired. The status quo contract gives her extra flexibility to respond to negative income shocks. However, if clients have present biased preferences \textit{and} are sophisticated about them, they may choose the frequent payment contract as it has commitment value. This value would be traded off against the value of lost flexibility. This design also allows us to test the extent to which commitment must be externally imposed and reinforced to be effective, relative to softer and more self-directed forms of commitment.   %Promises could have larger or smaller commitment value than a pecuniary fee, something that we test by comparing behavior in the \textit{promise-forcing} vs \textit{status quo} arms.

@@

The administrative data contains a unique identifier of the client, an identifier of the piece she is pawning, and the transactions relating to that piece. In particular, the value of the piece as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn. Within the period fo the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e. the client lost her pawn), and whether any late-payment fees (active for the relevant experimental arms) were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended. Figure \ref{exp_description}(a) shows the timing of the experiment and our admin data coverage. The black arrows represent the dates for which we have administrative data (before and after the experiment) for each branch, while the light gray segments represent the duration of the experiment. The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawn

In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a 5 minute survey \textit{before} going to the teller window to appraise their piece and before they were told contract terms (i.e. before treatment status was known). It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 10,437 clients.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).

@@

The study is subject to two potential forms of attrition.  The more serious is that clients would change their pawning decisions in response to the treatment arms.  If this were the case, our study would still recover internally valid estimates of the impacts of the treatment arms for the lender, but would not provide \textit{ceteris paribus} impacts on a comparable pool of individuals. We anticipated this possibility and trained appraisers to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.   Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day.\footnote{Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments. Lender P also never complained to us that our different treatments were hurting sales. The data support this story as well.}

@@

Finally, we also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active. To this end we estimated the regression\footnote{We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after. We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=1.32$, $\beta_b=-0.65$, with p-values 0.11 and 0.83, respectively).

All the pieces of evidence indicate that there was no selection across arms and that experimental comparisons are internally valid.

@@

%\subsection{The Choice of Commitment}
%\label{choice_commitment}

%Section \ref{fee-commitment} showed that the Forced Commitment commitment contract reduced financing cost across the board, and that consumers themselves seemed to like it once they tried it. In such a case, one would expect a strong demand for it. This is not the case. We also find that clients in the choice arm achieved no better outcomes than those in the status quo group.

%\subsection{Demand for the Forced Commitment commitment contract} \label{sec:demand}

%\noindent \textbf{Low demand for commitment:} 
We begin our empirical analysis with a comparison of the Forced Commitment and Commitment Choice arms to the control.  In the Forced arm, all individuals received the Commitment product.  In the Choice arm, 11\% of individuals offered the product selected it.  When preferences or income streams are heterogeneous, and consumers are neoclassical, giving choice among contracts is often a welfare increasing strategy. Consumers would choose the contract that best fits their needs. This holds also in most simple models of present bias preferences if consumers are sophisticated about their present bias. 
But when consumers are overconfident about their ability to save to pay back the loan, free choice could be a sub-optimal policy from the point of view of the client's long run self, and could match clients with  more costly contracts.   In this sense, if this self-selection mechanism works perfectly (as it would in a Roy model with all hyperbolics sophisticated) then the Forced and Choice arms will have an identical effect.  Deviations between the impacts of these two arms therefore are implicitly a test of the optimality of the choices made in the choice arm.

@@

Would clients benefit ---in terms of recovering their pawn and in terms of paying lower financing cost--- from having a monthly payment commitment contract \textit{forced} on them, vis-a-vis the status quo pay-when-you-want contract? We find they do. For each comparison, we separately estimate the regression equation (\ref{basic_reg}) below.

\begin{equation} \label{basic_reg}
    y_{ij} = \alpha + \beta T_{i} + \gamma X_{ij} + \epsilon_{ij}
\end{equation}

\noindent where $i$ refers to client, $j$ indexes branch, and $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment. Results are robust to excluding them. In the regressions we include them and add a dummy indicating clients who has more than one treatment in the experimental period.} %\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, as well as an indicator variable for client $i$ losing her pawn. In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect. We cluster errors at the branch-day level.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}

The Intention to Treat (ITT) results are very clear:  giving clients the option of choosing commitment is not effective, and forcing them into the commitment contract is.  Choice does \textit{not} lead to lower financial cost compared to the status-quo contract. Nor does it lead to higher pawn recovery.  Figure \ref{main_te} gives the standardized effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.  Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.

\textcolor{red}{Include here table that has regressions from Eq. 1 underlying the figure above.}

\vspace{.2in}
\noindent \textbf{Detailed analysis of financial cost.} Figure \ref{fc_pro4} digs in more detail into the sources of variation underlying the main effects in Figure \ref{main_te}.   $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost. The leftmost coefficient corresponds to plugging into the formula of section \ref{FC_def} the appraised gold value of the pawned piece. The second coefficient uses the subjective value of the pawn instead. In both cases we find that being assigned to the Forced Commitment commitment contract causes a large reduction in the financing cost the client incurred, of 9.4\% (\$297) under the first definition and 13.2\% (\$472) under the second one. That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.

Financial cost incurred by pawn-shop clients is a key variable to study. However it does not take into account transportation cost or the opportunity cost of going in person to the branch. Given that the Forced Commitment contract makes clients visit the branch more often (monthly), one may want a measure that includes those costs as well. Going in that direction, in a broader measure of costs, for each visit we add the self-reported transport cost plus a whole day's wage, multiplied by the number of visits. Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and some precision from missing data on transportation costs. We conclude that penalizing borrowers for delinquency in a contract which has already has large penalties from default (losing the collateral in a highly collateralized loan) actually helps borrowers.

>>>>

Pawn loans involve individuals leaving valuable and liquid assets, typically jewelry, as collateral in exchange for an immediate cash loan. Collateral is typically larger than the loan, which allows lenders to skip the checking of credit history and give the loan immediately. This makes pawn loans a popular way to get cash to pay for emergencies. In fact, they are one of the most prevalent forms of borrowing. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues.\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender alone served more than 1 million clients in the last 3 years with more than 4 million contracts. For comparison there were 2.3 million micro-finance clients across all lenders in Mexico in 2009 \citep{Pedroza:2010}.

Pawning is also one of the oldest forms of borrowing. Pawn lending existed in antiquity at least since the Roman Empire, and there are records of it in China about 1,500 years ago \citep{PawnShops}. In spite of the high prevalence and long history, pawnshop borrowing has not received much attention in the economics literature. The closest product widely studied is payday loans. In developing countries, however, payday lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash. According to \cite{Payday} to get a payday loan: ``All that a prospective borrower typically needs is a home address; a valid checking account; a driver’s license and Social Security number; a couple of pay stubs to verify employment; wages and pay dates; and minimum earnings of at least \$1,000 a month''. Although the author meant this list as an instance of low requirements, they would render virtually all poor households in the developing countries ineligible.

@@

As with payday lending, pawnshop lending is controversial. Regulators have concerns with the sophistication of borrowers using it. The US congress has actually banned the payday lending industry from serving active military personnel, and some States in the US have imposed zoning restrictions, interest caps, and restrictions on serial borrowing as consumer protection measures against payday lending \citep{Payday}. The main source of concern is whether consumers that use these loans suffer from behavioral and cognitive biases which imply sub-optimal choices. There is some evidence  in support of this view.\footnote{\cite{Bertrand} write that ``Under the view that the people borrowing from payday lenders are making an informed, utility-maximizing choice given the constraints that they face, one  would not expect additional information disclosure about the payday product to  alter their borrowing behavior'', but to the contrary they find that simply disclosing how financing costs add up reduced demand by 11\%. \cite{Meltzer} finds that payday loan access leads to increased difficulty paying mortgage, rent and utilities bills.}   Our study reinforces the idea that a lack of sophistication may be an integral part of that way that standard pawn contracts are structured.

@@

Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period, and the client could make payments at anytime with no penalty for pre-payment. No reminders or interim contact exists between the lender and the borrower.  If the client returns to pay the principal plus the accumulated interest within 105 days, she received back her pawn, otherwise the pawnbroker kept the piece and any payments made. Before the contract expired, the client had the right to renew it  using the same collateral for another 3 months by going to the pawnshop paying the accumulated interest and signing a new contract with exactly the same terms as the original one.  26\% of borrowers renew at least once with a given pawn. This contract was standard in the industry.

The clients that pawned understood these terms well (as we verified in interviews). \footnote{90\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.  This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months. They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.  When asked why they are pawning this piece 5\% responded `lost a family member', `a medical emergency' (11\%), or `an urgent expense' (71\%).

Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.   One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report in our baseline survey that they anticipate recovering the pawn at the time they take the loan.   High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer. Lender P was explicitly interested in  partnering with us to investigate whether a frequent payment contract would increase pawn recovery, costumer satisfaction, and repeat borrowing, and to explore whether there was demand for such a contract.

Pawnshops therefore makes money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non defaulted loans, and by keeping the payments made on defaulted loans. In this way the interest rate typically used to calculate borrower APRs is thus a very inadequate measure of the effective cost of pawn loans.

@@

\vspace{.2in}
\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the behavioral literature on the ways to improve repayment in credit contracts, it enhances the regularity and salience of payments. It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was reinforced in two ways; first by reminders issued to any borrower delinquent on the monthly payments that they were supposed to be made, and secondly by the levying of a nominal fee (2\% of minimum due) that would be levied on individuals behind in their payments.\footnote{This fee was set by the lender, being deemed to be large enough to reinforce commitment but small enough that if clients had an emergency and could not pay, the fee would not cause the pawn to be unrecoverable.  In contrast with \cite{John} we don't let the clients choose the size of the fee. That paper shows that doing this results in wrong choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment, as explained in the introduction. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
}

As is typical in the behavioral literature we include an arm that allows borrowers to opt in to the commitment contract if they choose.  If, however, a lack of sophistication is an issue with borrowers in pawn contracts, then this process of self-selection may not assign commitment to the `right' people.  To examine this issue, we include an arm  that assigns all individuals to the commitment contract so that we are able in essence to form three counterfactual outcomes; no commitment, commitment, and the chosen commitment.  This design allows us to investigate the repercussions of choice not only for those who \textit{do} choose (as is the case in a standard LATE design), but also the implications of choice for those who \textit{do not} choose.  This turns out to be key for what we can learn from this experiment.  In order to explore lower-cost forms of structure, we also include arms that feature `soft' commitment, asking or requiring individuals to follow the more regular payment structure of the commitment contract but then providing no reminders or repercussions for failing to do so.

@@

We did not allocate equal number of days across arms, since we were interested in having more power in some of them. The number of branch days allocated to each were 84, 80, 93, 68, and 82, respectively.  See Figure \ref{exp_description} for a CONSORT-style diagram of the study design and recruitment.

\vspace{.2in}
\noindent \textbf{Randomization.}  Starting September 6, 2012, we implemented the experiment in 6 branches of Lender $P$. The branches were selected by Lender $P$ to be dispersed across Mexico City and have varying sizes. In four of them the experiment ran for 107 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size. %Thus we eliminated {the smallest} ones. 
Branches are more than 5 km apart from each other, and there is little substitution among them; only 1\% of consumers appear in more than one of our branches.

 Branch personnel did not know which treatment would happen on which day. They were told that there were 5 different ``types of contract-days'' and that the system chose randomly which applied on any given date, and that it could happen for instance that two consecutive dates had the same contract. They were also told that this way of operating was in place in various Lender P's branches (they did not know which ones), and that it could be in place for several months. Randomizing at the day level limits the problem of contamination arising from clients realizing that other clients get different contracts than theirs. It also limits potential manipulation by appraisers, who in the presence of individual level randomization could potentially pick their preferred costumers from the line or tell them to wait until their desired contract shows up on the screen. Intra-branch day correlation on the probability of default (ICC) is small, at {0.08}, so we lose little power vis-a-vis individual-level randomization.

@@

The administrative data contains a unique identifier for the client, an identifier for the piece she is pawning, and the transactions relating to that piece. In particular, the value of the piece as assessed by the appraiser, the amount of money loaned (70\% of the value), the date of the pawn transaction, and the type of contract for that pawn. Within the period of the loan, we followed each transaction related to that piece in the administrative data: when payments were made and for what amounts, whether there was default (i.e. the client lost her pawn), and whether any late-payment fees were imposed. After the experimental loan, we are able to track subsequent behavior and to see whether that borrower took a subsequent loan.  We have this information for all the pawns that occurred in the experiment's 6 branches between August 2, 2012 and August 13, 2013, this includes all the pawns under our experiment but also those that happened 1 month before it started and up to 8 months after it ended. Figure \ref{exp_description} shows the design and timing of the experiment, along with the sample sizes in each arm. The experiment comprises 13,446 pawns, and our administrative data cover a total of 23,974 pawn

In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a 5 minute survey \textit{before} going to the teller window to appraise their piece and before they were told contract terms (i.e. before treatment status was known). It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 10,437 clients, and the survey response rate is 78\%.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
%Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).

@@

The study is subject to two potential forms of attrition.  The more serious is that clients would change their pawning decisions in response to the treatment arms.  If this were the case, our study would still recover internally valid estimates of the impacts of the treatment arms for the lender, but would not provide \textit{ceteris paribus} impacts on a comparable pool of individuals. We anticipated this possibility and trained appraisers to say --that whatever was the contract that day-- it was the only available contract for an undetermined amount of time.   Because we do not observe refusals directly, we address this issue by examining the number of borrowers per day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day.\footnote{Our enumerators informed us that potential clients rarely left the branch without pawning, and that it was even less common that they did so when hearing about monthly installments. Lender P also never complained to us that our different treatments were hurting sales. The data support this story as well.}

@@

Finally, we also tested if the number of pawns per day for the 6 branches that participated in the experiment was different 1 month before the experiment started or 1 month after the experiment ended, relative to the days the experiment was active. To this end we estimated the regression\footnote{We cluster the standard errors by branch.} $Pawns \: per \: day_{jt} = \alpha_j + \gamma f(t) + \beta_b \mathbbm{1}(t \in MB)_{t} +\beta_a \mathbbm{1}(t \in MA)_{t}$, where $\alpha_j$ are branch fixed effects, $f(t)$ is a third degree polynomial in time, $\beta_b$ measures a level effect in the number of pawns per branch a month before the experiment started, and $\beta_a$ a month after. We estimate no difference in the number of pawns, showing that people are not leaving the branch without pawning at larger rates during the experiment ($\beta_a=1.32$, $\beta_b=-0.65$, with p-values 0.11 and 0.83, respectively).  Table \ref{num_pawns_bal} shows the beta coefficients from these regressions, which are nowhere significant.  Hence we begin the analysis confident that differential attrition has not occurred.

@@

the comparison of the \textit{Commitment Choice} arm to the \texit{Control} arm provides the test of self-selection that is standard in the behavioral literature.  A lack of impact in this comparison would be consistent either with a population of neo-classical borrowers, for whom the commitment feature is superfluous, or with a population of time-inconsistent borrowers who lack sophistication over their own behavioral problems.  The key to distinguishing these two stories is the treatment effect of commitment on those who would not choose it; this counterfactual is revealed through the comparison of the \textit{Forced Commitment} arm to the \textit{Control}.  So while the forcing of commitment cuts against the grain of a behavioral literature that has largely promoted `nudges', it reveals important additional information that will be particularly relevant in borrower populations that are both hyperbolic and naive.

As a starting point for the empirical analysis, in the Choice arm only 11\% of individuals offered the product selected it. This is initial evidence either that we are dealing with a population of largely time consistent individuals who do not need commitment, or of a population with many naive individuals who do not know that they need it.  If this self-selection mechanism works perfectly (as it would in a Roy model with all hyperbolics sophisticated) then the Forced and Choice arms will have an identical effect.  Deviations between the impacts of these two arms therefore are implicitly a test of the optimality of the choices made in the choice arm.

We pose this question using the standard Intention to Treat analysis equation (\ref{basic_reg}) across arms.

\begin{equation} \label{basic_reg}
    y_{ij} = \alpha + \beta^F T_{i}^F + \beta^C T_{i}^C + \gamma X_{ij} + \epsilon_{ij}
\end{equation}

\noindent where $i$ refers to client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Fixed or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment. Results are robust to excluding them. In the regressions we include them and add a dummy indicating clients who has more than one treatment in the experimental period.} We cluster errors at the branch-day level. %\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, which we further decompose into its component costs:  payments to capital, fees, interest, and the cost of losing the pawn.  We then cast each of these costs as an Annual Percentage Rate (APR).  as well as an indicator variable for client $i$ losing her pawn. In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}

@@

The Intention to Treat (ITT) results, presented in Table \ref{main_impact_table} and graphically in Figure \ref{main_te}, are extremely stark.  The Choice arm fails to deliver improvements on any measure (with the exception of an increase in fees, for which we are very powered since this outcome is always zero in the control).  In sharp contrast, the Forced Commitment arm yields very strongly significant decreases in the financial cost of loans to clients.  Despite causing a 106 peso increase in payments to capital and a 28 peso increase in fees, the Forced arm leads to a 100 peso decline in interest payments and an enormous decline in the expected pawn losses (almost 500 pesos), driven by a 12\% decrease in the probability of default.  The bottom panel of the figure casts these costs as APRs, and shows that while the Choice arm actually leads to a slight \textit{increase} in the APR, the Forced arm decreases the effective annualized interest rate of pawn lending by 40\%.   Figure \ref{main_te} gives the standardized effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.  Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.

There are other intermediate outcomes that are impacted by being assigned to frequent payments. Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the Forced Commitment arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).% Figure \ref{induced_to_pay_early} in the correlates HTE on financing cost with the HTE time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost. 
Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6). The percentage of the loan paid increases by 8 percentage points on average (column 7). However the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).

While the mechanical financial cost and APR incurred by pawn-shop clients are key outcomes, it is worth deepening the analysis with a set of additional drivers relevant to the subjective costs perceived by borrowers.  Figure \ref{robustness_fc} shows the results of these robustness checks.  First, rather than using the appraised value of the pawn from the lender, we can assess costs using the subjective value of the pawn reported by the borrower.  Second, because the Commitment contract requires more frequent visits to the branch, there are travel costs incurred relative to the status quo payment structure that we can include in the costs of commitment.  For each visit we add the self-reported transport cost plus a whole day's wage, multiplied by the number of visits. Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and some precision from missing data on transportation costs. Finally, we can adjust for the fact that the early payment induced by the commitment contract actually reduces the effective liquidity received by borrowers.  Taking the interest rate as the opportunity cost of capital, the interest payments averted are not really `saved' given that the liquidity is itself foregone.  So our final adjustment removes the saved interest payments from the calculation of the benefits across arms.  The figure shows the effects of each of these adjustments on the estimate of financial cost and APR, and illustrates that even when we make all of these adjustment simultaneously the Forced arm generates benefits of 0.11 standard deviations.
